### 2014-03-01 paper/real.tex
bigass footnote

JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
built-in functionality for I/O.
%
Consequently, and in contrast to our C and Haskell embeddings---for
which we must eliminate external effects---the embedding for JS is
trivial.
%
As a first step, we directly implement |specLangJS roundrobinf| by
running multiple instances of the JS runtime, i.e., |targetLangJS|, in
separate OS-level threads.

@@

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains reference.
%
Hence, as discussed in Section~\ref{sec:concrete} we restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects~\tocite{}.
%
In our formalization this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie') , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' ie)), ldots)
.->
iS'; sched S (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and Worker
communications~\tocite{}.
%
Insomuch, that the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

@@

To address this we use content security policy (CSP) and (iframe)
sandbox~\tocite{} to restrict external effects according to the label
of a task (Worker or browsing context), as describe
in~\tocite{}.
%
Of course, simply disallowing all external effects for all browsing
contexts would break most of the Web.
%
Hence SWAPI only enforces IFC, and thus restricts external effects,
when the JS code uses the new API.\footnote{
  Once a piece of code ``opts-in'' to use our IFC API, in addition to
  restricting external effects we interpose ``standard''
  \texttt{postMessage} communication to ensure that no information is
  leaked between contexts that have opted-in and those that have not.
}
%
Moreover, rather than disallowing all external effects, SWAPI allows
controlled network communication by leveraging the fact that web
pages already have an accompanying security policy: the same origin
policy.
%
Hence, for example, a Worker that has read data only sensitive to
\texttt{http://bank.ch} can communicate with this domain; only once
\texttt{http://aws.com} data is also included in the context will all
network requests be blocked.
%
Of course, this requires that we use a concrete label format to
express the policies; we refer the interested reader to~\tocite{} for
more details.

>>>>

JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
built-in functionality for I/O.
%
Consequently, and in contrast to our C and Haskell embeddings---for
which we must eliminate external effects---the embedding for JS is
trivial.
%
As a first step, we directly implement |specLangJS roundrobinf| by
running multiple instances of the JS runtime, i.e., |targetLangJS|, in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime event-loop, but the heap and
 execution context of each task is disjoint. This is similar to the
 single-heap language of Section~\ref{sec:concrete}.  However, since the heap
 separation is provided by the browser the browser, we do not discuss
 this further. The interested reader is referred to~\tocite{} for more
 details.
}

@@

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains reference.
%
As discussed in Section~\ref{sec:concrete} we thus restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects~\tocite{}.
%
In our formalization this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie') , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' ie)), ldots)
.->
iS'; sched S (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and Worker
communications~\tocite{}.
%
Insomuch, that the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

@@

To address this, we additionally use content security policy (CSP) and
(iframe) sandbox~\tocite{} to restrict external effects according to
the label of a task (Worker or browsing context), as describe
in~\tocite{}.
%
Of course, simply disallowing all external effects for all browsing
contexts would break most of the Web.
%
Hence SWAPI only enforces IFC, and thus restricts external effects,
when the JS code uses the new API.\footnote{
  Once a piece of code ``opts-in'' to use our IFC API, in addition to
  restricting external effects we interpose ``standard''
  \texttt{postMessage} communication to ensure that no information is
  leaked between contexts that have opted-in and those that have not.
}
%
Moreover, rather than disallowing all external effects, SWAPI allows
controlled network communication by leveraging the fact that web
pages already have an accompanying security policy: the same origin
policy.
%
Hence, for example, a Worker that has read data only sensitive to
\texttt{http://bank.ch} can communicate with this domain; only once
\texttt{http://aws.com} data is also included in the context will all
network requests be blocked.
%
Of course, this requires that we use a concrete label format to
express the policies; we refer the interested reader to~\tocite{} for
more details.
